Government through Patronage

### 2020-09-28 paper/paper.Rmd
incorporate latest changes

---
title: "Government through Patronage"
subtitle: "Bargaining for Education in Decentralized Brazil"
author: Galileu Kim
date: "`r gsub('^0', '', format(Sys.time(), '%d %B, %Y'))`"
documentclass: article
fontsize: 12pt
geometry: margin=1.5in
abstract: "Why do politicians engage in patronage? What are its consequences for public service delivery? I find that staff turnover in educational staff results from mayors attempt to exchange public sector jobs for support from local legislators. Leveraging fieldwork evidence and administrative data, I demonstrate that mayors with a weaker hold on the local legislature resort to patronage to co-opt legislators. Educational staff turnover has negative downstream effects on student learning, but limited electoral backlash. Weak electoral accountability channels suggests that patronage is primarily a political elite game, with little involvement by the electorate. These findings point to the dangers of elite capture of public services and its downstream consequences for social welfare."
header-includes:
  - \setlength\parindent{20pt}
  - \usepackage{setspace}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \usepackage{titling}
  - \usepackage{amsmath}
  - \DeclareMathOperator*{\argmax}{arg\,max}
  - \onehalfspacing
  # - \pretitle{\centering\Large\textbf}
  # - \preauthor{\centering\large}
  # - \predate{\centering\normalsize}
  - \usepackage[hang,flushmargin]{footmisc}
bibliography: dissertation.bib
output: 
  pdf_document:
    citation_package: biblatex
keep_tex: TRUE
biblio-style: authoryear
---
\pagebreak

>>>>

---
title: "Government through Patronage"
subtitle: "Bargaining for Education in Decentralized Brazil"
author: Galileu Kim
date: "`r gsub('^0', '', format(Sys.time(), '%d %B, %Y'))`"
documentclass: article
fontsize: 12pt
geometry: margin=1.5in
abstract: "Why do politicians engage in patronage and what are its consequences for public service delivery? I find that staff turnover in educational staff results from mayors attempt to exchange public sector jobs for support from local legislators. Leveraging fieldwork evidence and administrative data, I demonstrate that mayors with a weaker hold on the local legislature resort to patronage to co-opt legislators. Educational staff turnover has negative downstream effects on student learning, but limited electoral backlash. Weak electoral accountability channels suggests that patronage is primarily a political elite game, with little involvement by the electorate. These findings point to the dangers of elite capture of public services and its downstream consequences for social welfare."
header-includes:
  - \setlength\parindent{20pt}
  - \usepackage{setspace}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \usepackage{titling}
  - \usepackage{amsmath}
  - \DeclareMathOperator*{\argmax}{arg\,max}
  - \onehalfspacing
  # - \pretitle{\centering\Large\textbf}
  # - \preauthor{\centering\large}
  # - \predate{\centering\normalsize}
  - \usepackage[hang,flushmargin]{footmisc}
bibliography: dissertation.bib
output: 
  pdf_document:
    citation_package: biblatex
keep_tex: TRUE
biblio-style: authoryear
---
\pagebreak
